---
title: "CCA"
author: "DELEUZE, POULAIN, SCALA"
date: "2023-10-19"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

require(CCA)
require(GGally)
require(data.table)
dataset<-fread("sales.csv")
colnames(dataset) <- c("Sales_Growth", 
                       "Sales_Profitability", 
                       "New_Account_Sales", 
                       "Creativity", 
                       "Mechanical_Reasoning", 
                       "Abstract_Reasoning", 
                       "Mathematics")
summary(dataset)
psych <- dataset[, 1:3]
acad <- dataset[, 4:7]
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

